How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-22 tse-paper/content.tex
Mega review done

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on manually supplied example pairs of build logs and chunks, PBE automatically
  synthesizes
  a regular expression extracting the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  % TODO what is the vector space model
  Using the Vector Space Model, CTS selects lines of a log which are
  most similar to the lines present in manually supplied example chunks.
  \item \textbf{Keyword Search (KWS)}
  % TODO what is an ad-hoc method?
  Ad-hoc method for finding fitting passages by searching the whole
  text of a build log for
  the occurrence of specific trigger words.
\end{itemize}

@@

In short, this article contributes
\begin{itemize}
\item the first systematic study of the emerging field of build log analysis.
\item three prototypical open-sourced implementations of the most promising chunk retrieval techniques.
\item a large-scale empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
\item a detailed replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

In this section, we survey the emerging field of build log
analysis. We first start with a differentiation to the related field of general system log analysis. Then, we describe the methodology and results of a systematic mapping study to
determine the state-of-research on build log analysis following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}. 
We close by summarizing how build logs are commonly
analyzed in literature and discuss the implications of these findings.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the processing of system log
files produced during runtime of the system. The first difference here is that build logs are produced during runtime of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

% TODO In general, we should reference petersen2015guidelines a bit
% more. I.e., following the suggestions by Petersen or something, to
% show how we followed their protocol. This comment applies to the rest of this section

@@

To guide the data extraction we created a template. The template form contained questions to answer RQ 1.1 through RQ 1.3, for example ``Is the technique explained in sufficient detail?'' and ``What is the source of the build logs?'' As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a pilot study:
both authors extracted  data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors and inspected them as closely as necessary to fill out the template with confidence,
starting from occurrences of ``log'' or ``build'' within the article's text. For questions that did not require a boolean answer, we allowed assigning multiple tags or categories as the first part (``preparation phase'') of a virtual open card sorting~\cite{zimmermann2016card}. 
% TODO: add more concrete example, such as use of retrieved x: developer feedback, build data set
Once we had classified all works, we went into the second phase (``execution phase'') in which we found synonyms, and grouped tags together.

@@

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language Processing}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}

@@

% TODO repeat the question in the subsection title?
\subsubsection{Retrieved Information (RQ 1.1)}
% TODO General ref to Figure 4 missing: We answer this question along data in Figure 4, and ... ?

@@

% TODO It is unclear where this comes from. Also, wouldn't it perhaps be better to continue with Figure 4.b directly?
In most cases (51\%), a chunk was retrieved from the log.
Build logs were scanned for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, distinguishing failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

@@

% perhaps remove?
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported processing from two up to 122 million logs.

@@

% TODO A and B should possibly be overlapping, otherwise there is an area where neither A nor B makes sense?
\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producers.}
		\label{fig:litsur:log_producer}
\end{figure}

\subsection{Discussion}
\label{sec:lit-sur:discussion}

% TODO: this section is crucial. maybe we can highlight important findings, by categorizing them either as further subsubsections or making it bold in the text?
% TODO: find values for X and Y
Our literature survey shows that despite its relatively young age
(first occurrence of a paper on the topic in X), \textbf{build log analysis is
a widely established technique} in the literature, with Y articles on it.

@@

% TODO this is disconnected, at least here
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone'', other
articles pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.

@@

Our evaluation of the three chunk retrieval techniques is done on the
\emph{LogChunks} data set because it encompasses a broad range of
build environments which enables us to measure the generic
applicability of our techniques.
The targeted chunks are describing error messages or
``the reason the build failed'', which was also the information
most targeted by the articles in our survey.

@@

\Cref{tab:ctr} shows a comparison of the presented techniques.

@@

\subsection{Program Synthesis by Example (PBE)}
The concept of \emph{Programming by Example} aims to capture the
intent of the user through examples which they provide.
Leveraging this approach, we implemented a chunk retrieval technique
for build logs.
Our implementation is based and highly influenced by the
\emph{Microsoft PROSE library}~\cite{prose2019webpage}.
The PROSE library is powered by the generic program synthesis framework
\emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
Both enable us to synthesize regular expression programs
consistent~\cite{mitchell1982generalization} with a set of in-
and output examples given by the user.
The usage of example enables the user to configure a chunk
retrieval without understanding the whole structure of
the build log.

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
a substring of the log file text, representing the
substring that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
If PROSE cannot synthesize a program, e.g.\
because the regular expression
necessary would be too complicated to synthesize, PBE returns the
error message ``no program found''.
\Cref{lst:prose-program-simplified} presents a simplified version
of a program learned from the examples in \Cref{lst:chunk-example}.

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique based on the common
Vector Space Model~\cite{schutze2008introduction}.
The aim is to retrieve those lines from a build log which are most
similar to examples given by the user.

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% TODO Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
In our evaluation, we want to compare against a baseline of randomly
picking lines from the build log.
RLR mimics the
situation of guessing blindly which lines might be interesting.
The only configuration option for RLR is the number of lines it should
return.
For a fair comparison to the other techniques (whose number of
returned lines is dynamic), we configure RLR to return the average
number of lines in the chunks of the training examples.

% TODO Moritz: you said: some more details here?
% I would not know of any details to add.
%It's really all we are doing

\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

@@

When PBE is trained with these two examples, it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators,
which is consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3},
which has a
different structural representation, is added to the training set,
PBE is not able to synthesize a program and returns
``\texttt{no program found}''.
We later express this difference in structural representation through
dividing log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.
The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techniques.

@@

KWS is configured with keywords that appear close to the chunk within
the build log.
For the examples from \Cref{lst:chunk-example} these could be
``FAILURE'', ``wrong'' or ``failed''.
The example from \Cref{lst:chunk-example-3} could be found
by searching for ``FAIL''.
If KWS would be trained with all three examples and the aforementioned
associated keywords, it would search for the three keywords from
\Cref{lst:chunk-example}, as they appear twice---most often within
the training set of three examples.

\subsection{Tool Implementation}
For our comparison study, we implemented each of the chunk retrieval
techniques and a unifying interface.
The unified interface is implemented in Ruby and
calls the separate technique implementations over the command line.
The implementation of PBE in C\# is based on the Microsoft PROSE
library~\cite{prose2019webpage}.
We implemented CTS, KWS and RLR using
R and the text2vec library~\cite{text2vec2019webpage}.
They can be found in our replication
package~\cite{brandt2020chunk-replication} together
with Docker images which have
our techniques installed and ready to use.

\section{Study Design}
\label{sec:study}

To investigate when our chunk retrieval techniques are suited to
analyze build logs (\textbf{RQ2}), we perform an empirical comparison
study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
In particular, we are interested in how many examples a technique
should be trained with (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}) and how reliable the quality of the
produced outputs is (\textbf{RQ2.3}).

@@

\subsection{LogChunks}
For this study, we created the previously published data set
\emph{LogChunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''~\cite{brandt2020logchunks}.
We included keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

\subsection{Study Process}
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
same build environment (1).
One to five examples make up the training set (2).
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of our techniques
should receive reliable results on every build log they analyze.
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and our oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

>>>>

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on manually supplied example pairs of build logs and chunks,
  PBE automatically
  synthesizes
  a regular expression extracting the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  % TODO what is the vector space model?
  Using the Vector Space Model, CTS selects lines of a log which are
  most similar to the lines present in manually supplied example chunks.
  \item \textbf{Keyword Search (KWS)}
  % TODO what is an ad-hoc method?
  Ad-hoc method for finding fitting passages by searching the whole
  text of a build log for
  the occurrence of specific trigger words.
\end{itemize}

@@

In short, this article contributes
\begin{itemize}
\item the first systematic study of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of the most
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
\item a detailed replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

In this section, we survey the emerging field of build log
analysis.
We first start with a differentiation to the related field of general
system log analysis.
Then, we describe the methodology and results of a systematic mapping
study to
determine the state-of-research on build log analysis following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.

We close by summarizing how build logs are commonly
analyzed in literature and discuss the implications of these findings.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the processing of system logs produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in sufficient detail?'' and
``What is the source of the build logs?'' As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted	data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors
and inspected them as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.
For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.

% TODO: add more concrete example, such as use of retrieved x: developer
feedback, build data set
Once we had classified all works, we went into the second phase
(``execution phase'') in which we  grouped tags
together and found synonyms.

@@

% TODO: vertical alignment of rows with text to middle so they are aligned with pictograms on the right?
\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language Processing}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}

@@

% TODO repeat the question in the subsection title?
\subsubsection{Retrieved Information (RQ 1.1)}
% TODO General ref to Figure 4 missing: We answer this question along
% data in Figure 4, and ...
% ?

@@

% TODO It is unclear where this comes from.
% TODO Also, wouldn't it perhaps be better to continue with Figure 4.b directly?
In most cases (51\%), a chunk was retrieved from the log.
Build logs were scanned for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, distinguishing failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

@@

% TODO perhaps remove this paragraph?
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported processing from two up to 122 million logs.

@@

% TODO A and B should possibly be overlapping, otherwise there is an
% area where neither A nor B makes sense?
\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
		1.5cm 0.5cm},
		clip]{img/lit-sur/log_producer_annotated.pdf}
		\caption{Frequency of supported log producers.}
		\label{fig:litsur:log_producer}
\end{figure}

\subsection{Discussion}
\label{sec:lit-sur:discussion}
% TODO we are extracting failures in the following studies, which is mainly what
% literature does, too, right? Highlight here and mention later again

% TODO: this section is crucial.
% maybe we can highlight important findings, by categorizing them either
% as further subsubsections or making it bold in the text?
% TODO: find values for X and Y
Our literature survey shows that despite its relatively young age
(first occurrence of a paper on the topic in 2001, vast majority after
2016), \textbf{build log analysis is a widely established technique}
in the literature, with Y articles on it.

@@

% TODO this is disconnected, at least here
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' other
articles pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.

@@

Our evaluation of the three chunk retrieval techniques is done on the
\emph{LogChunks} data set because it encompasses a broad range of
build environments which enables us to measure the generic
applicability of our techniques.
The targeted chunks are describing error messages or
``the reason the build failed,'' which was also the information
most targeted by the articles in our survey.

@@

% TODO this is not enough for Table 3. Where does it come from?
% How did it originate? Also: never single sentence abstracts
\Cref{tab:ctr} shows a comparison of the implemented techniques.

% TODO Somehow, we have to find a better place for this. We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes to late. The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

@@

\subsection{Program Synthesis by Example (PBE)}
The concept of \emph{Programming by Example} aims to capture the
intent of the user through examples which they provide.
Leveraging this approach, we implemented a chunk retrieval technique
for build logs.
Our implementation is based on the
\emph{PROSE library}~\cite{prose2019webpage}.
The PROSE library is powered by the generic program synthesis framework
\emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
Both enable us to synthesize regular expression programs
consistent~\cite{mitchell1982generalization} with a set of in-
and output examples given by the user.
The usage of example enables the user to configure a chunk
retrieval without understanding the whole structure of
the build log.

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example; we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
a substring of the log file text, representing the
substring that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
If PROSE cannot synthesize a program, e.g.,\
because the regular expression
necessary would be too complicated to synthesize, PBE returns the
error message ``no program found.''
% TODO Figure 7 should not come before Figure 6. Figure 6 and 7 should be
% introduced first. This is best-practice anyway: Whenever you mention
% a figure/table the standard sentence should always be: Figure X shows Y,
% on the vertical axis Z and on the horizontal axis D.

\Cref{lst:prose-program-simplified} presents a simplified version
of a program learned from the examples in \Cref{lst:chunk-example}.

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% TODO Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique based on the common
% TODO: the ominuous Vector Space Model again ...
Vector Space Model~\cite{schutze2008introduction}.
The aim is to retrieve those lines from a build log which are most
similar to examples given by the user.

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% TODO Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% TODO: I think it is good, but the VSM is still unexplained. We need a
% (at least) 1-sentence introduction to it, at its first reference
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
% TODO: could you add two-three more references to the results of RLR in
% the discussion, to show how even seemingly low numbers are much better
% than RLR?

To fully comprehend how difficult a task build log analysis really is without any a-priori knowledge, we include a comparison with a base line generated by Random Line Retrieval (RLR), that is,
picking lines randomly from the build log.
RLR mimics the
situation of guessing blindly which lines might be interesting.
The only configuration option for RLR is the number of lines it should
retrieve.
For a fair comparison to the other techniques (whose number of
returned lines is dynamic), we configure RLR to return the average
number of lines in the chunks of the training examples, thus arguably giving it a slight advantage.

% TODO Moritz: you said: some more details here?
% I would not know of any details to add.
%It's really all we are doing
% TODO: You are right, nothing more is necessary

% TODO: these next two sections do not belong under this section -- they are not a chunk retrieval technique. One way to fix it would be to rename the section.
\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

@@

When PBE is trained with these two examples, it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators,
which is consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3},
which has a
different structural representation, is added to the training set,
PBE is not able to synthesize a program and returns
``\texttt{no program found}.''
We later express this difference in structural representation through
dividing log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.
The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techniques.

@@

KWS is configured with keywords that appear close to the chunk within
the build log.
For the examples from \Cref{lst:chunk-example} these could be
``FAILURE,'' ``wrong,'' or ``failed''.
The example from \Cref{lst:chunk-example-3} could be found
by searching for ``FAIL.''
If KWS was to be trained with all three examples and the aforementioned
associated keywords, it would search for the three keywords from
\Cref{lst:chunk-example}, as they appear twice---most often within
the training set of three examples.

\subsection{Tool Implementation}
For our comparison study, we implemented each of the chunk retrieval
techniques and a unifying interface.
The unified interface is implemented in Ruby and
calls the separate technique implementations over the command line.
We implemented PBE in C\# based on the Microsoft PROSE
library~\cite{prose2019webpage} and CTS, KWS, and RLR using
R and the text2vec library~\cite{text2vec2019webpage}.
% TODO and passive again ...
The source code of the implementation can be found in our replication
package~\cite{brandt2020chunk-replication} together
with ready-to-use Docker images.

\section{Study Design}

% TODO This section is not structured well. First, it misses an
% explanation of the bigger study design.  Second, What is the difference between Study Process and
% Study Design? Third, the LogChunks section appears out of nowhere
% and is not related to the section title (different abstraction
% level).  Perhaps a solution would be to be a bit inspired by this
% paper:
% https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
% There is a research design section (which we are missing) and a
% Research Method section (which is a mixture of the current section
% titled Log Chunks and Study Process)

\label{sec:study}

To investigate when the chunk retrieval techniques are suited to
analyze build logs (\textbf{RQ2}), we perform an empirical comparison
study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
In particular, we are interested in how many examples a technique
should be trained with (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}) and how reliable the quality of the
produced outputs is (\textbf{RQ2.3}). This leads us to the following research questions:

@@

\subsection{LogChunks}
To conduct the study in this paper, we created the 
\emph{LogChunks}  data set~\cite{brandt2020logchunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''.
We included keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

### 2020-04-22 tse-paper/paper.tex
Mega review done

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

>>>>

% The paper headers
\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.
